---
title: "IGBD"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load the package.
library(igdb)
```

The IGDB package provides access to the [IGDB API](https://api.igdb.com/) which gives information on video games, developers, reviews, companies, and other related content.

## Install

Use devtools to install from Github.

```{r, eval = FALSE}
devtools::install_github("jonathande4/igdb")
```

## Usage

At the time of this package was developed, most of the available API endpoints are covered. These include:

* `igdb_characters`: [Characters](https://igdb.github.io/api/endpoints/character/)
* `igdb_collections`: [Collections](https://igdb.github.io/api/endpoints/collection/)
* `igdb_companies`: [Company](https://igdb.github.io/api/endpoints/company/)
* `igdb_credits`: [Credits](https://igdb.github.io/api/endpoints/credit/)
* `igdb_franchises`: [Franchise](https://igdb.github.io/api/endpoints/franchise/)
* `igdb_games`: [Game](https://igdb.github.io/api/endpoints/game/)
* `igdb_genres`: [Genre](https://igdb.github.io/api/endpoints/genre/)
* `igdb_keywords`: [Keywords](https://igdb.github.io/api/endpoints/keyword/)
* `igdb_pages`: [Pages](https://igdb.github.io/api/endpoints/page/)
* `igdb_platforms`: [Platform](https://igdb.github.io/api/endpoints/platform/)
* `igdb_pulses`: [Pulse](https://igdb.github.io/api/endpoints/pulse/)
* `igdb_reviews`: [Reviews](https://igdb.github.io/api/endpoints/review/)

Each function follows a similar format.

* `search`: title or keyword relating to kinds of results you want to return.
* `id`: each element in the api has an associated id. If you know the id of the game, review, or company you can pass that as a single number or vector of numbers to retrieve only those elements.
* `n`: maximum number of results to return.
* `limit`: maximum number of results per page.
* `scroll`: an alternative method for pagination which allows you to request more than 10,000 rows ([see pagination](https://igdb.github.io/api/references/pagination/)).
* `filter`: a method for narrowing search results (e.g `"[created_at][gt]=2017-01-01"`) ([see filters](https://igdb.github.io/api/references/filters/)).
* `fields`: a vector of columns the api should return.
* `order`: a string that sets the order of the results (e.g `created_at:asc`, `name:desc`)
* `api_key`: an API key provided when you sign up.

You can find the full documentation for the API [here](https://igdb.github.io/api/about/welcome/).

## API Key

Before you can begin to use the service, [sign up](https://api.igdb.com/signup) and receive an API key. Once you have your key, you can pass it to the function parameter `api_key` or use

```
Sys.setenv("IGDB_KEY" = 'YOUR_API_KEY`)
```

to add it to your environment. The function `igdb_key()` will look in the system environment for a variable with that name.

## Examples

### Games

```{r}
# Returns games matching "bioshock" but filters games released after 2015.
igdb_games(
  search = "bioshock",
  order = "first_release_date:asc",
  filter = "[first_release_date][lt]=2016-01-01",
  fields = c("id", "name", "first_release_date", "rating", "popularity")
  )
```

### Companies

```{r}
igdb_companies(
  search = "2k",
  order = "start_date:desc",
  fields = c("id", "name", "start_date", "published"),
  n = 20
  )
```

### Reviews

```{r}
igdb_reviews(
  search = "bioshock",
  fields = c("username", "created_at", "title", "game", "views", "platform")
)
```


### Characters

```{r}
igdb_characters(
  search = "booker dewitt"
)
```

### Filtering Results

To get results for specific games, use the filter options.

```{r, eval = FALSE}
# Filter on slug value.
igdb_games(filter = "[slug][eq] = bioshock-infinite")

# Filter on game id.
igdb_reviews(filter = "[game][eq] = 538")
```

## Known Quirks

#### Queries with No Results

In some cases if there are no results, the API will issue a 404 reponse causing a function error.

```{r, error = TRUE}
igdb_genres(search = "action")
```

#### Scroll Issue

Scrolling may also not work always work as expected with smaller queries. We still get the first 50 results, but not as many as expected. R will issue a warning when this happens. For better results, switch to pagination using offset.

```{r}
# Pagination with Scroll.
games <- igdb_games("halo", scroll = TRUE, n = 100)
NROW(games)

# Pagination with offset.
games <- igdb_games("halo", scroll = FALSE, n = 100)
NROW(games)
```


## Contributing

If you find any bugs, you can file an issue or create a pull request. Each function was created using the same basic template. As long as there are no breaking api changes, adding new endpoints should be simple.
